### 2022-11-09 NSF2022/Description/backgroundv2.tex
SA1 getting there

\begin{figure}
  \begin{center}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize {\em Left:} In the HAP
  formulation, a system of exterior problems defines the hydrodynamic
  and hydrophobic interactions. {\em Right:} Particles translate and
  rotate to lower the free energy $F[u]$ subject to \eqref{eq:SL}, $f(u)
  = u^2$, and reach a minimal configuration in panel C. The colormap is
  blue for $u = 0$ and red for $u = 1$. The arrows are the velocity
  field $\mathbf{u}$.}
\end{figure}

@@

Finally, we mention that in the single-well case
$W(\phi) = \tfrac{1}{2}u^2,$ \eqref{eqn:phase} takes the form
of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
If the material label $h_i = 1$ everywhere, then $\phi$
has a boundary layer going from $1$ at the boundary to $0$ in the bulk
and one can prove that 
\begin{equation}
\label{eqn:math_motivation}
\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS
\end{equation}
under the assumption that $\Omega$ has a class $\mathbf{C}^2$ boundary \cite{}.
In other words, the phase energy can be viewed as an
approximation of surface energy that ``extends'' into the bulk.
In the general case, $h_i^2$ replaces $1$ in \eqref{eqn:math_motivation}.
We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
is a correct description of long-range surface interactions.

>>>>

\begin{figure}
  \begin{center}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize {\em Left:} In the HAP
  formulation, a system of exterior problems defines the hydrodynamic
  and hydrophobic interactions. {\em Right:} Particles translate and
  rotate to lower the free energy $F[u]$ subject to \eqref{eq:SL}, $W(\phi)
  = \phi^2$, and reach a minimal configuration in panel C. The colormap is
  blue for $u = 0$ and red for $u = 1$. The arrows are the velocity
  field $\mathbf{u}$.}
\end{figure}

@@

Finally, we mention that in the single-well case
$W(\phi) = \tfrac{1}{2}\phi^2,$ \eqref{eqn:phase} takes the form
of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
If the material label $h_i = 1$ everywhere, then $\phi$
has a boundary layer going from $1$ at the boundary to $0$ in the bulk
and one can prove that 
\begin{equation}
\label{eqn:math_motivation}
\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS
\end{equation}
under the assumption that $\Omega$ has a class $\mathbf{C}^2$ boundary \cite{}.
In other words, the phase energy can be viewed as an
approximation of surface energy that ``extends'' into the bulk.
In the general case, $h_i^2$ replaces $1$ in \eqref{eqn:math_motivation}.
We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
is a correct description of long-range surface interactions.
